---
title: "STA 5250 Homework 10"
author: "Daniel Silva"
date: "Due 11/16/21"
output:
    pdf_document:
      df_print: kable
---

```{r global_options, include=FALSE}
# these are some optional settings that will change how some features look
# you do not need to change them.
knitr::opts_chunk$set(out.width = "65%", out.height="65%", fig.align="center", warning=FALSE, message=FALSE)
```


### Loading Relevant Packages

```{r}
# load any relevant packages here, if necessary
library(fpp3)
library(astsa)
```


# Question 3


```{r}
q5_data <- hh_budget %>% filter(Country == "Australia")

q5_data %>% gg_tsdisplay(difference(Debt),"partial")

fit3 <- q5_data %>% 
  model(m1 = ARIMA(Debt ~ pdq(2,1,2)),
        m2 = ARIMA(Debt ~ pdq(2,1,1)),
        m3 = ARIMA(Debt ~ pdq(3,1,1)),
        m4 = ARIMA(Debt ~ pdq(1,1,1)),
        search = ARIMA(Debt,stepwise=FALSE,approximation = FALSE))

glance(fit3) %>% arrange(AICc)

fit3 %>% select(search) %>% gg_tsresiduals()

augment(fit3) %>% 
    features(.innov,ljung_box)

```

## auto = ARIMA(1,1,0) w/drift

(i) Yes, the residuals look like they have mean zero.

(ii) Yes, the residuals seem like they have close to constant variance.

(iii) There is no significant autocorrelation among the residuals.

(iv) Yes, it look normally distributed

(v) Yes, 0.96 is high enough to pass the Ljung-Box test.


# Question 4

```{r}
unemprate_ts <-as_tsibble(UnempRate)

unemprate_ts %>% gg_tsdisplay(difference(value,12),"partial",lag_max = 65)

fit4 <- unemprate_ts %>% 
  model(m1 = ARIMA(value ~ pdq(2,0,1)+PDQ(4,1,0),order_constraint = P>3),
        m2 = ARIMA(value ~ pdq(2,0,2)+PDQ(4,1,0),order_constraint = P>3),
        m3 = ARIMA(value ~ pdq(3,0,0)+PDQ(4,1,0),order_constraint = P>3),
        search = ARIMA(value,stepwise=FALSE,approximation = FALSE))

fit4$search

glance(fit3) %>% arrange(AICc)

fit3 %>% select(search) %>% gg_tsresiduals()

augment(fit3) %>% 
    features(.innov,ljung_box)
```

## auto = ARIMA


# Question 5

## Part (a)



## Part (b)



## Part (c)








# Question 6

## Part (a)



## Part (b)



## Part (c)



## Part (d)













